\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Moiz Arif} \\ \vspace{1pt}
    \small Accelerated Computing Architect $\cdot$ AI Infrastructure $\cdot$ GPU Systems \\ \vspace{4pt}
    \href{mailto:moizarif2002@gmail.com}{\underline{moizarif2002@gmail.com}} \ $|$ \
    \href{https://linkedin.com/in/moizarif2002}{\underline{linkedin.com/in/moizarif2002}} \ $|$ \
    \href{https://github.com/moizarif}{\underline{github.com/moizarif}}
\end{center}

%-----------SUMMARY-----------
\section{Summary}
Accelerated computing systems engineer with deep expertise in AI infrastructure. With a Ph.D.\ in Computing and Information Sciences, I specialize in designing and optimizing GPU-centric systems for AI workloads. My work spans memory hierarchy optimization, distributed AI training, LLM inference pipelines, and CXL-based memory expansion --- bridging the gap between cutting-edge research and production infrastructure.

Currently focused on GPU-centric AI infrastructure, LLM inference optimization, and memory hierarchy research for accelerated computing systems.

%-----------SKILLS-----------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{AI/ML}{: CUDA, PyTorch, TensorFlow, TensorRT, LLM Inference, RAG Systems} \\
     \textbf{Systems}{: CXL, HBM, MPI, Distributed AI, GPU Profiling} \\
     \textbf{Cloud/Infra}{: Kubernetes, OpenStack, AWS, Azure, GCP}
    }}
 \end{itemize}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Micron Technology}{2023 --- Present}
      {Principal Engineer, System Design Architect}{}
      \resumeItemListStart
        \resumeItem{Architected GPU-centric AI infrastructure and accelerated computing systems for LLM inference and HPC workloads.}
        \resumeItem{Optimized AI inference workflows by analyzing KV-cache behavior, model offloading strategies, and GPU memory bottlenecks.}
        \resumeItem{Benchmarked memory hierarchy trade-offs across HBM, DDR5, LPDDR, NVMe, and CXL expansion memory.}
        \resumeItem{Characterized VectorDB-backed RAG pipelines on NVIDIA GPU platforms.}
      \resumeItemListEnd

    \resumeSubheading
      {Rochester Institute of Technology}{2019 --- 2023}
      {Graduate Research Assistant}{}
      \resumeItemListStart
        \resumeItem{Developed infrastructure-aware TensorFlow scheduling for heterogeneous datacenters improving ML performance by 54\%.}
        \resumeItem{Designed CXL-aware intelligent memory systems for GPU-bound workloads.}
        \resumeItem{Published research across ISCA, SC, IPDPS, and ICPP in accelerated computing and memory systems.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Rochester Institute of Technology}{Rochester, NY}
      {Ph.D. in Computing and Information Sciences}{2019 --- 2023}
      \resumeItemListStart
        \resumeItem{Research focus: GPU computing, memory hierarchy optimization, distributed AI systems, and large-scale AI infrastructure.}
      \resumeItemListEnd

    \resumeSubheading
      {National University of Sciences and Technology (NUST)}{Islamabad, Pakistan}
      {M.S. Electrical Engineering --- Telecom \& Computer Networks}{Aug 2015}

    \resumeSubheading
      {National University of Computer and Emerging Sciences (NUCES)}{Islamabad, Pakistan}
      {B.S. Telecommunications Engineering}{Aug 2011}

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
  \resumeSubHeadingListStart

    \resumeSubheading
      {LLM Inference Optimizer}{}
      {CUDA, PyTorch, Python, TensorRT}{}
      \resumeItemListStart
        \resumeItem{A framework for analyzing and optimizing KV-cache behavior and model offloading strategies in large language model inference pipelines.}
      \resumeItemListEnd

    \resumeSubheading
      {CXL Memory Disaggregation System}{}
      {C++, CXL, Linux Kernel, HPC}{}
      \resumeItemListStart
        \resumeItem{Research prototype for CXL-based memory expansion enabling GPU workloads to leverage disaggregated memory pools across datacenter nodes.}
      \resumeItemListEnd

    \resumeSubheading
      {Distributed AI Training Platform}{}
      {TensorFlow, Kubernetes, Python, MPI}{}
      \resumeItemListStart
        \resumeItem{Infrastructure-aware scheduling system for distributed TensorFlow training across heterogeneous GPU clusters with 54\% performance improvement.}
      \resumeItemListEnd

    \resumeSubheading
      {RAG Pipeline Benchmarking Suite}{}
      {Python, NVIDIA GPU, VectorDB, RAG}{}
      \resumeItemListStart
        \resumeItem{Comprehensive benchmarking framework for evaluating VectorDB-backed Retrieval-Augmented Generation pipelines on NVIDIA GPU platforms.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PUBLICATIONS-----------
\section{Publications}
Research focus: GPU acceleration, distributed AI systems, heterogeneous computing, CXL memory architectures, AI infrastructure optimization, and HPC systems.

\begin{itemize}[leftmargin=0.15in]
    \item Understanding Inference Scaling for LLMs: Bottlenecks, Trade-offs, and Performance Principles --- ISCA 2026
    \item Evaluating Expansion Memory for Optimizer State Offloading for Large Transformer Models --- IPDPS 2025
    \item Application-Attuned Memory Management for Containerized HPC Workflows --- IPDPS 2024
    \item Accelerating Performance of GPU-based Workloads Using CXL --- FlexScience 2023
    \item Canary: Fault-tolerant FaaS for Stateful Time-sensitive Applications --- SC 2022
    \item Exploiting CXL-based Memory for Distributed Deep Learning --- ICPP 2022
\end{itemize}

%-----------RESEARCH AREAS-----------
\section{Research Areas}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
    \textbf{GPU Systems $\cdot$ AI Infrastructure $\cdot$ Memory Hierarchy $\cdot$ Distributed AI} \\
    My research explores the intersection of hardware architecture and AI systems --- from optimizing GPU memory hierarchies and CXL-based memory expansion to building scalable infrastructure for distributed AI training and inference at scale.
    }}
\end{itemize}

%-----------CERTIFICATIONS-----------
\section{Certifications}
\begin{itemize}[leftmargin=0.15in]
    \item Mirantis Certified Administrator for OpenStack
    \item PLUMgrid Certified OpenStack Networking Associate
    \item AWS Solutions Architect Training
    \item Veeam Sales Professional (VMSP)
    \item Cisco CCNA Training
\end{itemize}

%-----------AWARDS-----------
\section{Awards}
\begin{itemize}[leftmargin=0.15in]
    \item Outstanding Graduate Student Award --- RIT, 2022
    \item HPDC Student Travel Grant --- 2023
    \item BrickHack 8 Winner --- Best Use of Google Cloud, 2021
    \item IEEE Member
    \item ACM Member
\end{itemize}

\end{document}
